Software Citation Principles

### 2016-03-16 sc-principles/software-citation-principles.tex
adding a paragraph on software peer review in 5

>>>>

\textbf{Software peer review}

This document does not discuss peer review of software, which is an important issue but is
also mostly out of scope in the context of software citation principles.
Since the goal of software citation is to identify the software
that has been used in a scholarly product, whether or not that software has been peer-reviewed
is irrelevant.  One possible exception would be if the peer-review status of the software should
be part of the metadata, but the working group does not believe this to be part of the
minimal metadata needed to identify the software.
